Coherent optical association of a single molecule -- Supplemental material

### 2020-11-12 sm.tex

\section{Calculating Matrix Elements with Coupled Channel Ground State}
To calculate Rabi frequencies for transitions to intermediate vibrational levels of the c$^3\Sigma\ (\Omega=1)$ electronic state, we
obtain their wavefunctions from a single-channel calculation using the potential curve of \cite{Grochola2011}. We
then calculate overlap integrals between this function and the triplet ($S=1$) components of the
coupled-channel wavefunctions for either the target molecular state or the confined atomic state.
These calculations assume that the intermediate state has pure triplet character and neglect its
nuclear spin character, which is unknown.

>>>>

\section{Calculating Matrix Elements with Coupled Channel Ground State}
To calculate Rabi frequencies for transitions to intermediate vibrational levels of the c$^3\Sigma^+ (\Omega=1)$ electronic state, we
obtain their wavefunctions from a single-channel calculation using the potential curve of \cite{Grochola2011}. We
then calculate overlap integrals between this function and the triplet ($S=1$) components of the
coupled-channel wavefunctions for either the target molecular state or the confined atomic state.
These calculations assume that the intermediate state has pure triplet character and neglect its
nuclear spin character, which is unknown.
